---
title: "ComputingProjectAAT"
output: html_document
---
#installing the packages in order to display and measure the size of objects in images. #These packages will be used to run codes that will measure the area of the C.Elegans in different pictures. These measurements will analyze the growth of different C.Elegan's groups to determine the effect of vapor administration. -Tori
```{r}
library(PythonInR)
library(graphics)
install.packages("imager")
```

```{python}

from scipy.spatial import distance as dist
from imutils import perspective 
from imutils import contours 
import numpy as np 
import argparse 
import imutils
import cvb

```

```{python}
```{python}
# import the necessary packages
from scipy.spatial import distance as dist
import numpy as np
import matplotlib
```

#the package imageJ (by Anna) was imported and used to measure the area (in 10^-4 mm) of the C.Elegans in each photo. The data set was collected from the image analysis and imported as Worm_Size_Results

#analyzing Worm_Size_Results data using an anova test-Tori
```{r}
C.elegansresults <- aov(C.Elegans~Area, data=Worm_Size_Results)
summary(C.elegansresults)
```
#I created a simple plot of the data set.-Tori
```{r}
plot(C.Elegans~Area, data=Worm_Size_Results)
```

#I creaed a TukeyHSD test of the data - Ashley 
```{r}
TukeyHSD(C.elegansresults)
```
#this woud have been the t.test that needed to be done originally before it was decided to do an ANOVA test instead - Ashley
```{r}
t.test(C.elegansresults)
```

