---
title: 'Final R Notebook'
output: html_notebook
---
Final Notebook for Anna Harmon, Ashley Huebert, and Tori Schooler's Computing Project 

#Tori's Portion: Installing Packages for Image Analysis
#research on different packages that could be installed that could analyze and measure the E.Coli of Anna Harmon's images from her capstone project. 
#possible packages include imager with R, and scipy, numpy, opencv, matplotlib, and imutils with Python. 
#With little success with these packages and codeblocks below, Anna installed the package ImageJ and can be seen in her portion below. 
```{r}
library(PythonInR)
library(graphics)
install.packages("imager")
```

```{python}
from scipy.spatial import distance as dist
from imutils import perspective 
from imutils import contours 
import numpy as np 
import argparse 
import imutils
import cvb

from scipy.spatial import distance as dist
import numpy as np
import matplotlib
```

#Anna's Portion: Installing and Using ImageJ for Image Analysis

#Tori's Portion: Running and AOV test and plot 
#The data and areas of E.Coli measured from the ImageJ analysis was analyzed using an anova test. 
```{r}
C.elegansresults <- aov(C.Elegans~Area, data=Worm_Size_Results)
summary(C.elegansresults)
```

```{r}
plot(C.Elegans~Area, data=Worm_Size_Results)
```

#Ashley's Portion: Running TukeyHSD 


