---
title: 'Final R Notebook'
output: html_notebook
---
Final Notebook for Anna Harmon, Ashley Huebert, and Tori Schooler's Computing Project 

#Tori's Portion: Installing Packages for Image Analysis
#research on different packages that could be installed that could analyze and measure the E.Coli of Anna Harmon's images from her capstone project. 
#possible packages include imager with R, and scipy, numpy, opencv, matplotlib, and imutils with Python. 
#With little success with these packages and codeblocks below, Anna installed the package ImageJ and can be seen in her portion below. 
```{r}
library(PythonInR)
library(graphics)
install.packages("imager")
```

```{python}
from scipy.spatial import distance as dist
from imutils import perspective 
from imutils import contours 
import numpy as np 
import argparse 
import imutils
import cvb

from scipy.spatial import distance as dist
import numpy as np
import matplotlib
```

#Tori's Portion: Running and AOV test and plot 
#The data and areas of E.Coli measured from the ImageJ analysis was analyzed using an anova test. 
```{r}
C.elegansresults <- aov(C.Elegans~Area, data=Worm_Size_Results)
summary(C.elegansresults)
```

```{r}
plot(C.Elegans~Area, data=Worm_Size_Results)
```
#Anna's Portion: Installing and Using ImageJ for Image Analysis
#Uploaded the images into RStudio as well as ImageJ. Using ImageJ, I measured around each worm at 200% magnification for accurate tracing and, with the measuring option, was given a value for each worm that correlated to size. I put these values into an Excel sheet and averaged the size for each worm. I then uploaded the Excel into our GitHub (as well as emailed copies to Ashley and Tori) so that Ashley and Tori could do their portions of the project.


#Ashley's Portion: Running TukeyHSD 
```{r}
TukeyHSD(C.elegansresults)
```

```{r}
t.test(C.elegansresults)
``` 

#I created a TukeyHSD test of the data and the t.test would have been the test that was needed originally before it was decided to do an ANOVA test instead 
